---
title: "Care And Feeding"
author: "Jeff"
date: "8 juillet 2016"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 

## R and RStudio Updates

RStudio and/or Shiny updates are a regular occurance; when they happen, sometimes dplyr package has a hard time updating, fails, or doesn't launch again. I don't know if this is only on Windows or not.

I have generally resolved this by running this script in the RStudio console:

```{r}
if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}
devtools::install_github("hadley/lazyeval")
devtools::install_github("hadley/dplyr")

if (!require("devtools"))
  install.packages("devtools")
devtools::install_github("rstudio/shiny")
```

This forces the packages to update directly from github and to recompile on the local instance (where the console is running). Note that if this is done on the R server instance, the console where the script is run must be open on the remote server.




