---
title: "Data Import Template"
author: "Jeff Norville"
date: "12 juillet 2016"
output: 
  word_document: 
    fig_caption: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import Format

This document describes the data import for the Verification Score database.

Each "deposit" of data into the database needs to be structured so the system stays "tidy" and the imports remain as automated as possible.

## Guidelines

We've designed the Loader application to accept text or Rdata files, to help guide the user through the import, but there are also some rules for the data you should know upfront:

1. Names shouldn't exceed 200 characters (*and* the longer the name, the funnier the plots look)
2. Required fields may be relied on to link to other data elements, or to calculate time or date ranges, etc. Please be as complete (and precise) as possible.
3. Optional fields are ... self-explanatory
4. If you make a mistake, that's fine -- but the nature of this database doesn't make corrections easy! You'll need to "turn off" your entire submission and do a second one, and the old submission will eventually be "garbage collected" out of the database

# Rdata Format (.rds)

The methods to read and save **.rds** files is a little different from the standard Rdata file format, though it's useful to understand the difference.

```{r eval=FALSE}
?readRDS
?saveRDS

```



## Field names

I try to adhere to R naming conventions. Accordingly, I avoid spaces, "CamelCase", and use periods (.) to seperate terms. However, you can use most characters in your variable names; the following are NOT permitted: 
```
$, #, quotes, comma, _ (underscore)
```

Fields are...  | or:
---------------|--------------
*optional*     | **mandatory**

Optional fields may either be left blank or ommitted.

### Fieldname list
*  **location.name**
*  *provider.firstname*
*  *provider.lastname*
*  **provider.organization.name**
*  **provider.email**
*  **provider.phone**
*  **forecast.system**
*  **forecast.frequency**
*  **lead.time.interval**
*  member.count
*  **mean.error**
*  **start.date**
*  **end.date**
*  *members*
*  **lead.times**
*  **timestep**

### Style guides
Just one of many style guides:

https://google.github.io/styleguide/Rguide.xml


### Download example file

*Link to it here:*

proto.Rds

-----

# Text File Format(s)


Some users may use their own systems to output scores and avoid using R; the Loader supports imports from CSV (classically "comma-seperated value") files as well as text files in teh same format.

There are two sections to each file:

1. **Metadata**
   + start.date
   + end.date
   + timestep
   + provider.firstname
   + provider.lastname
   + provider.organization.name
   + provider.email
   + provider.phone
   + forecast.system
   + forecast.frequency
   + lead.time.interval
   + member.count

2. **Data**
   + location.name
   + mean.error
   + lead.times

## Departure from Rds file

The Rds file import provides a less-complicated internal validation process, and is encouraged. However, it may be more complicated - or impractical - to implement for some users.

For smaller dataloads, text file and/ or Excel file uploads may work most efficiently.

However, note that only ONE SCORE TYPE may be submitted for each file import. Subsequent loads may be copy/pasted into the same file format, maintaining (largely) the same metadata.


## Download example file

Link:

1. CSV file
2. DAT file
3. Excel file


# Technical Details 
Loading score files -- whether text (CSV or tab-delimited file) or Rds file format -- is done using the Shiny "Loader" tool. This is linked through the datamining tool website, or available directly from RStudio / github (*link*).

The metadata are used to identify the 

 * data source
 * provider contact details
 * case study details
 * model type (aka forecast system)
 * 

## File Size Limit
Upper size limit: 60 mb

This size limit is imposed by the server; larger files take more time to upload, process, and potentially cause user frustration. 

Note that the Rds datafile format is binary, compressed, and more "efficient" than (for example) a CSV (text) file. A 50 mb Rds file could be several hundred mb as text.

## File Verification

There is a light "verification" step during file upload; however, it's up to the loader to verify what the Loader echoes is correct. If the upload needs correction, cancel the upload and make corrections directly on your file.

If the Loader has already been run when you catch an error, the entire "deposit" must be flagged (for automatic garbage collection).



-----

# More Reading

For more insights into the data format you can read this document:

