---
title: "Notes Week 18"
author: "Jeff"
date: "2 mai 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
readRenviron("~/R/.Renviron")
REdbname = Sys.getenv('pgdb')
REuser = Sys.getenv('api_user')
REpassword = Sys.getenv('pgpassword')
#db connections
library(dplyr)
library(ggplot2)
db <- src_postgres('postgres',
                   host = 'localhost',
                   port = 5432,
                   user = REuser,
                   password = REpassword)
tbl_scores <- tbl(db, "tblScores")
```

## Week 18, 2016 (week 9 of the internship)
I've finally begun this journal (weekly, actually, or hebdo en français), though as it's taken two months to get "comfortable"" with R it's late in the process. Onward quand même! 
The idea will be to compile todo lists and accomplishments in a running narration of the work.

This (short 3 day) week I have these goals:

* update shiny plot as function with inputs:
    + this score
    + average score

* add query types to shiny interface
* test with "seasonal" and monthly timescales
* create "interface tables" to speed interface queries (locations, etc)


```{r db}
# dbsub <- filter(tbl.scores, dateValue > "2005-01-01" & dateValue < "2005-12-31")
dbsub <- filter(tbl_scores, datePartValue == 5 & dataPackageGUID == "SMHI2222")
db2005 <- collect(dbsub)
summary(db2005)
```

## Including Plots

Subset of data:
```{r }
sm <- subset(db2005, locationID %in% c('9504667', '9540863') ) # & scoreType == "Seasonal_LS_month" c('S2242510')
summary(sm)

```


My plot de jour:

```{r lead time plot, echo=FALSE}
ggplot(sm,aes(x = leadtimeValue , y = datePartValue)) +
  geom_point(aes(color = scoreValue), size=3) +
  scale_x_continuous("Lead Time (weeks)") + # scale_y_date("Months of 2005 (January omitted)") +
  scale_color_gradient(low="yellow", high="darkgreen")
```

Sub-subset of data (lead time = 5 days):
```{r plot summary 1}
smsub <- filter(sm, LT==5)
summary(smsub)

```

```{r line plot 1, echo=FALSE}
#sm <- subset(db2005, locationID %in% c('S2242510') & scoreType == "Seasonal_LS_month")
ggplot(smsub,aes(y = (smsub$scoreValue-mean(smsub$scoreValue))/mean(smsub$scoreValue), x = dateValue)) +
  geom_line(aes(color = 'red'), size=1) +
  scale_y_continuous("scores") + scale_x_date("time")

# +
#   scale_color_gradient(low="yellow", high="darkgreen")
```

Sub-subset of data (lead time = 10 days):
```{r plot summary 2}
smsub <- filter(sm, LT==10)
summary(smsub)

```

```{r line plot 2, echo=FALSE}
#sm <- subset(db2005, locationID %in% c('S2242510') & scoreType == "Seasonal_LS_month")
ggplot(smsub,aes(y = (smsub$scoreValue-mean(smsub$scoreValue))/mean(smsub$scoreValue), x = dateValue)) +
  geom_line(aes(color = 'red'), size=1) +
  scale_y_continuous("scores") + scale_x_date("time")
# +
#   scale_color_gradient(low="yellow", high="darkgreen")
```


Note - perhaps x axis should be time from start rather than an actual date ?

Note 2016-09-04 - attempted to "update" from final database version, but since LC's daily ECMWF data is no longer in DB it's really not an interesting effort